Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-25 chapters/introduction/introduction.tex
edits before geo-calibration for feature learning section

\section{Background}
For a better understanding of our work, before the discussion of the
main topics, we would like to introduce some related computer vision
concepts in this section.

@@

\subsection{Deep Learning in Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas. 
It is widely accepted that DNNs have excellent performance in
high-level visual feature learning.
This valuable ability provides researchers powerful tools to
solve the challenging geo-calibration tasks.
Weyand and Kostrikov \etal~\cite{planet} propose a convolutional
network to predict the geographic location of the input
image. Walch \etal~\cite{walch2017image} aggregate learned CNN
features with LSTM to generate global image representation for camera
localization.  In pose estimation aera, Work~\cite{zhai2016horizon,
workman2016horizon, hold2017perceptual} has been done to identify
the horizon line with CNNs (one can derive the camera roll and pitch
angles from the horizon line position giving the camera focal length).

@@

>>>>

\section{Background}
For a better understanding of our work, we would like to introduce
some related computer vision concepts in this section before the
discussion of the main topics.

@@

In conclusion, most of the geo-calibration algorithms we mention above
relies on finding visual cues from the input images. The development
of these algorithms require strong human expertise about the data,
thus can only be applied in limited scenarios. Therefore, researchers
need new methodologies in order to make the development of
geo-calibration algorithms more efficient.

\subsection{Deep Learning in Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas. 
It is widely accepted that DNNs have excellent performance in
high-level visual feature learning.
This valuable ability provides researchers powerful tools to
solve the challenging geo-calibration tasks.
Weyand and Kostrikov \etal~\cite{planet} propose a convolutional
neural network (CNN) to predict the geographic location of the input
image. Walch \etal~\cite{walch2017image} aggregate learned CNN
features with LSTM to generate global image representation for camera
localization.  Studies about camera pose
estimation~\cite{zhai2016horizon, workman2016horizon,
hold2017perceptual} has been done by identifying the horizon line with
CNNs (one can derive the camera roll and pitch angles from the horizon
line position giving the camera focal length).

@@

These geo-calibration methods make the predictions directly out of
DNNs.  There is another big category of geo-calibration methods that
use aerial imagery as geo-registered database, which we will introduce
in the following section.
